Test susieI using chr17 to 22

### 2020-08-28 analysis/index.Rmd
visual chr17to22
susieI
susieI all regions

@@

>>>>

# Test parameters for susie
 * [Using UKbiobank data (chr17:22), fusion weights Adipose, test prior's effect for susie](simulation-multi-ukbchr17to22-gtex.adipose_susieprior.html)

@@

## mr.ash + SUSIE iterative
*  [Using UKbiobank data (chr17:22), fusion weights Adipose](simulation-susieI-ukbchr17to22-gtex.adipose.html)

### 2020-08-28 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
susieI all regions

# susieI genes

Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3 , and also require at least one causal gene or SNP is present, also, at least one gene.

@@

Results for each region:
```{r regions}
regionlist <- readRDS(paste0(outputdir, tag, "_regionlist.rds"))
ng <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene", , drop = F ])[1]))
ns <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "SNP", , drop = F ])[1]))
ng.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene" & x$ifcausal == 1, , drop = F])[1]))
ns.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "SNP" & x$ifcausal == 1, , drop = F])[1]))
ngdf <- data.frame("ngene" = ng, "nsnp" = ns, "ncausalgene" = ng.c, "ncausalSNP" = ns.c)

cat("causal gene fraction:", sum(ngdf$ncausalgene)/sum(ngdf$ngene) )
cat("causal snp fraction:", sum(ngdf$ncausalSNP)/sum(ngdf$ns))

for (i in seq(1, Niter, 10)){
  resf <- paste0(outputdir, tag, ".", i, ".susieIres.Rd") 
  load(resf)
  ngdf[, paste("Prior.gene", i)] <- unlist(lapply(gene.rpiplist, "mean"))
  ngdf[, paste("Prior.SNP", i)] <- unlist(lapply(snp.rpiplist, "mean"))
}
ngdf
```

@@

```{r param}
show_param <- function(tags){
  mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt" )
  param <- do.call(rbind, lapply(mr.ashfs, function(x) t(read.table(x))[2:1,]))

@@

  susieIfs <- paste0(outputdir, "20200813-", tags, ".susieIres.Rd" )
  param.s <- do.call(rbind, lapply(susieIfs, function(x) {load(x); c(tail(prior.gene_rec, 1), tail(prior.SNP_rec,1))}))

  susieIfs <- paste0(outputdir, "20200813-", tags, ".1.txt")
  param.s.truth <- do.call(rbind, lapply(susieIfs, function(x) {
    a <- read.table(x, header = T);
    c(nrow(a[a$ifcausal == 1 & a$type == "gene", , drop = F])/ nrow(a[a$type == "gene", , drop = F]),
      nrow(a[a$ifcausal == 1 & a$type == "SNP", , drop = F])/ nrow(a[a$type == "SNP", , drop = F]))
    }))

@@

  df <- cbind(pars, pars.s)
  rownames(df) <- tags

  df %>% 
  kable(format = "html", col.names = colnames(df)) %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")

@@

tags <- paste(rep(1:3, each = 5), 1:5, sep ="-")

show_param(tags)
```

# susieI shuffle genes
# one example
Shuffle genes to different regions.

@@

Results for each region:
```{r regions shuffle}
regionlist <- readRDS(paste0(outputdir, tag, "_regionlist.rds"))
ng <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene", , drop = F ])[1]))
ns <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "SNP", , drop = F ])[1]))
ng.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene" & x$ifcausal == 1, , drop = F])[1]))
ns.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "SNP" & x$ifcausal == 1, , drop = F])[1]))
ngdf <- data.frame("ngene" = ng, "nsnp" = ns, "ncausalgene" = ng.c, "ncausalSNP" = ns.c)

cat("causal gene fraction:", sum(ngdf$ncausalgene)/sum(ngdf$ngene))
cat("causal snp fraction:", sum(ngdf$ncausalSNP)/sum(ngdf$ns))

for (i in seq(1, Niter, 10)){
  resf <- paste0(outputdir, tag, ".", i, ".susieIres.Rd") 
  load(resf)
  ngdf[, paste("Prior.gene", i)] <- unlist(lapply(gene.rpiplist, "mean"))
  ngdf[, paste("Prior.SNP", i)] <- unlist(lapply(snp.rpiplist, "mean"))
}
ngdf
```

>>>>

# susieI genes - setting 1

* Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3, and also require at least one causal gene or SNP is present, also, at least one gene.

* Susie run parameters: `L=1`, `null_weight = 0`, didn't update `null_weight` in iterations.

@@

@@

```{r param}
show_param <- function(mrashfs, susieIfs, susieIfs2){
  param <- do.call(rbind, lapply(mr.ashfs, function(x) t(read.table(x))[2:1,]))

@@

  param.s <- do.call(rbind, lapply(susieIfs, function(x) {load(x); c(tail(prior.gene_rec, 1), tail(prior.SNP_rec,1))}))

  param.s.truth <- do.call(rbind, lapply(susieIfs2, function(x) {
    a <- read.table(x, header = T);
    c(nrow(a[a$ifcausal == 1 & a$type == "gene", , drop = F])/ nrow(a[a$type == "gene", , drop = F]),
      nrow(a[a$ifcausal == 1 & a$type == "SNP", , drop = F])/ nrow(a[a$type == "SNP", , drop = F]))
    }))

@@

  df <- cbind(tags, format(pars, digits = 4), format(pars.s, digits =4))
  rownames(df) <- NULL

  df %>% 
  kable("html", escape = F) %>%
  kable_styling("striped", full_width = F) %>%
  scroll_box(width = "100%")

@@

tags <- paste(rep(1:3, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".1.txt")

show_param(mrashfs, susieIfs, susieIfs2)
```

# susieI genes - setting 2

* Regions: All regions.

* Susie run parameters: `L=1`. Initiate with `null_weight = 0` and update `null_weight` based on last iteration results.

Prior change for each iteration:
```{r iter2}
load(paste0(outputdir, tag, ".config1.susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

## More examples

```{r param2}
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config1.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config1.susieI.txt")

show_param(mrashfs, susieIfs, susieIfs2)
```

# susieI genes - setting 3

* Regions: All regions.

* Susie run parameters: `L=2`. Initiate with `null_weight = 0` and update `null_weight` based on last iteration results.

Prior change for each iteration:
```{r iter3}
load(paste0(outputdir, tag, ".config2.susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

## More examples

```{r param3}
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config2.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config2.susieI.txt")

show_param(mrashfs, susieIfs, susieIfs2)
```

# susieI genes - setting 4

* Regions: All regions.

* Susie run parameters: `L=1`. Did not update `null_weight` in each iteration.

Prior change for each iteration:
```{r iter4}
load(paste0(outputdir, tag, ".config3.susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

## More examples

```{r param4}
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config3.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config3.susieI.txt")

show_param(mrashfs, susieIfs, susieIfs2)
```

# susieI shuffle genes
## one example
* Shuffle genes to different regions. Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3 , and also require at least one causal gene or SNP is present, also, at least one gene.

* Susie run parameters: `L=1`, `null_weight = 0`.

@@
